Measuring the double-drift illusion with hand trajectories

### 2021-12-11 Manuscript.Rmd
made fig 6 use same language as some paragraphs in the discussion

---
title: "Measuring the double-drift illusion with hand trajectories"
author: 
- Bernard Marius 't Hart 1,*
- Denise Y.P. Henriques 1
- Patrick Cavanagh 1,2,3
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: template.docx
  pdf_document: default
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{amsmath}
bibliography: bibliography.bib
csl: journal-of-vision.csl
link-citations: yes
---

@@

```{r fig6, echo=FALSE, message=FALSE, fig.width=6, fig.height=4, fig.cap="\\label{fig:fig6}**Figure 6:** Spontaneous resets without hand trajectories. Experiment and Results based on data from Liu et al. [-@Liu2021], re-analyzed here. **A:** By ensuring the perceived path of a double-drift stimulus is straight down (teal arrows), any gap-induced reset, should be equal to the accumulated illusion if there are no spontaneous resets (black arrow), but smaller if there are (light blue arrow). Gaps were presented after 1, 2 or 3 seconds, and 2 or 4 dva real paths, which allows psychophysics to quantify the amount of illusion left after several periods of observing a double-drift stimulus. **B:** Points of subject equivalence show that the size of the illusion decreases with time even as the real path, and maximum illusion is kept constant. These data are in line with resets occurring randomly over time. The simplest model presented by Liu et al. (2021) keeps the illusion strength constant and fits a chance of reset per time unit as ~0.007 / 10 ms to match the gap-evoked reset (diamond symbols)."}
plotJumpPSEs(target = 'inline', individualDots = FALSE, modelDots = TRUE, gammaDots=TRUE)
```

>>>>

---
title: "Measuring the double-drift illusion with hand trajectories"
author: 
- Bernard Marius 't Hart 1,*
- Denise Y.P. Henriques 1
- Patrick Cavanagh 1,2,3
output:
  pdf_document: default
  word_document:
    reference_docx: template.docx
  html_document:
    df_print: paged
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{amsmath}
bibliography: bibliography.bib
csl: journal-of-vision.csl
link-citations: yes
---

@@

```{r fig6, echo=FALSE, message=FALSE, fig.width=6, fig.height=4, fig.cap="\\label{fig:fig6}**Figure 6:** Spontaneous resets without hand trajectories. Experiment and Results based on data from Liu et al. [-@Liu2021], re-analyzed here. **A:** By ensuring the perceived path of a double-drift stimulus is straight down (teal arrows), any gap-induced reset, should be equal to the accumulated illusion if there are no spontaneous resets (black arrow), but smaller if there are (light blue arrow). Gaps were presented after 1, 2 or 3 seconds, and 2 or 4 dva real paths, which allows psychophysics to quantify the amount of illusion left after several periods of observing a double-drift stimulus. **B:** Points of subject equivalence show that the size of the illusion decreases with time even as the real path, and maximum illusion is kept constant. These data are in line with resets occurring randomly over time. The simplest model presented by Liu et al. [-@Liu2021] keeps the illusion strength constant and fits a chance of reset per time unit as ~0.7 / _s_ to match the gap-evoked reset (diamond symbols)."}
plotJumpPSEs(target = 'inline', individualDots=FALSE, modelDots=FALSE, gammaDots=FALSE, modelLine=TRUE, gammaLine=TRUE)
```
